Pre/Post-Trikafta

### 2022-01-19 Christine Chan/Pre-post Trikafta/pre_post_trikafta.Rmd
Update pre_post_trikafta.Rmd
functions for averaging by pre and post

```{r closest date function}
closest_dates = function(df,start = "Start",date = "Date"){
  # Start and date columns must be formated for subtraction (ideally with lubridate)
  df$Timepoint = as.numeric(df[,date] - df[,start])
  # Remove visits on start date or > 1 year out
  df = df %>% filter(Timepoint !=0 & abs(Timepoint) <= 365) %>% 
    # Get closest visit before and closest after
    group_by(CFF.ID,sign(Timepoint)) %>%
    slice_min(Timepoint * sign(Timepoint),n=1) %>% 
    # Format
    ungroup %>% select(-Timepoint) %>% rename(Timepoint = `sign(Timepoint)`)
  # Timepoint as factor
  df$Timepoint = factor(df$Timepoint,labels = c("Before","After"))
  # Delete unnecessary columns
  df = df %>% select(-all_of(c(start,date)))
  # Return
  df = data.frame(df)
  return(df)
} 
```

>>>>

```{r closest date function}
closest_dates = function(df,start = "Start",date = "Date"){
  # Remove MRN
  df$MRN = NULL
  # Start and date columns must be formated for subtraction (ideally with lubridate)
  df$Timepoint = as.numeric(df[,date] - df[,start])
  # Remove visits on start date or > 1 year out
  df = df %>% filter(Timepoint !=0 & abs(Timepoint) <= 365) %>% 
    # Get closest visit before and closest after
    group_by(CFF.ID,sign(Timepoint)) %>%
    slice_min(Timepoint * sign(Timepoint),n=1) %>% 
    # Format
    ungroup %>% select(-Timepoint) %>% rename(Timepoint = `sign(Timepoint)`)
  # Timepoint as factor
  df$Timepoint = factor(df$Timepoint,labels = c("Before","After"))
  # Delete unnecessary columns
  df = df %>% select(-all_of(c(start,date))) %>% select(CFF.ID,Timepoint,everything())
  # Return
  df = data.frame(df)
  return(df)
} 
pre_post_average = function(df,start = "Start",date = "Date"){
  # Remove MRN
  df$MRN = NULL
  # Start and date columns must be formated for subtraction (ideally with lubridate)
  df$Timepoint = as.numeric(df[,date] - df[,start])
  # Columns to exclude
  excluded_vars = c(start,date,"CFF.ID","Timepoint","sign(Timepoint)")
  # Remove visits on start date or > 1 year out
  df = df %>% filter(Timepoint !=0 & abs(Timepoint) <= 365) %>% 
    # Get closest visit before and closest after
    group_by(CFF.ID,sign(Timepoint)) %>%
    summarise(across(-any_of(excluded_vars), ~mean(.x,na.rm = T)),.groups = "drop") %>%
    # Format
    rename(Timepoint = `sign(Timepoint)`) %>%
    mutate_all(~replace(., is.nan(.), NA)) # Replace NaN
  # Timepoint as factor
  df$Timepoint = factor(df$Timepoint,labels = c("Before","After"))
  # Select
  df = df %>% select(CFF.ID,Timepoint,everything())
  # Return
  df = data.frame(df)
}
```
